### 2019-06-17 2-Chapters/2-Chapter/chapter2.tex
Probably enough for today? ALmost done for everything in Ch1 but the details of our contributions

\TODOL{Intégrer commentaires d'Emilie !}

@@

\textbf{Applications for Opportunistic Spectrum Access.}
% Detail the previous work from our team SCEE on bandits + OSA : Wassim, Navik
%
As highlighted in Chapter~\ref{chapter:1},
the focus of this work is on cognitive radio and IoT networks, where arms can represent wireless orthogonal channels, but more generally any resource characterizing the communication between a wireless device and a gateway (\eg, spreading factor for LoRa \cite{KerkoucheAlami18}, power allocation for NOMA etc).
% In cognitive radio using centralized supervision, for instance if the gateway can decide the allocation of devices to resources, MAB can also be used to let the gateway explore different allocations and learn by itself a good allocation, see for instance this article that consider 5G-like networks with small cells \cite{Maghsudi16}.
%
% Previous works of our SCEE team showed that MAB can be used to model the problem of spectrum access for a secondary user accessing a licensed spectrum.
% In this model, arms represent a finite set of orthogonal channels, \ie, different frequency bands in a licensed spectrum.
In the model of Opportunistic Spectrum Access (OSA) with sensing, the samples $Y_{k,t}$ represents the feedback obtained by the CR-equipped device after sensing the channel $k$ at time $t$.
A reward of $r(t) = 1$ indicates that no Primary User was sensed, while a reward of $r(t)=0$ indicates that the channel $k$ is busy at time $t$ and no uplink message can be sent.
%
This model was first introduced by Wassim Jouini during his PhD thesis,
in \cite{Jouini09} and later studied in both \cite{Jouini10,Jouini12}.
Proof-of-concepts using real-world radio hardware was first proposed in \cite{MoyWSR2014,RobertSDR2014}.
%
We study a similar model of using MAB for Cognitive Radio but without the OSA strucutre of Primary and Secondary users, \ie, without sensing information but only a collision indicator, in Chapters~\ref{chapter:4} and \ref{chapter:5}.

@@

% ----------------------------------------------------------------------------
\section{Definition, decomposition and lower-bounds on the regret}
% : definition, decomposition, and lower bounds
\label{sec:2:lowerUpperBoundsRegret}

@@

\subsection{Other measures of performances}

In this thesis, we only study analytically the mean regret $R_T^{\cA}$ (in Chapters~\ref{chapter:5} and \ref{chapter:6}), but we quickly mention other measures of performances used in our work.

>>>>

\TODOL{Intégrer les derniers commentaires d'Emilie, entre la fin des détails sur les familles exponentielles (avec les deux exemples), et quand je commence en Section~\ref{sub:2:otherMeasuresPerformance} à parler des autres mesures !}

@@

\textbf{Applications for Opportunistic Spectrum Access.}
% Detail the previous work from our team SCEE on bandits + OSA : Wassim, Navik
%
As highlighted in Chapter~\ref{chapter:1},
the focus of this work is on cognitive radio and IoT networks, where arms can represent wireless orthogonal channels, but more generally any resource characterizing the communication between a wireless device and a gateway (\eg, spreading factor for LoRa \cite{KerkoucheAlami18}, power allocation for NOMA etc).
% In cognitive radio using centralized supervision, for instance if the gateway can decide the allocation of devices to resources, MAB can also be used to let the gateway explore different allocations and learn by itself a good allocation, see for instance this article that consider 5G-like networks with small cells \cite{Maghsudi16}.
%
% Previous works of our SCEE team showed that MAB can be used to model the problem of spectrum access for a secondary user accessing a licensed spectrum.
% In this model, arms represent a finite set of orthogonal channels, \ie, different frequency bands in a licensed spectrum.
In the model of Opportunistic Spectrum Access (OSA) with sensing, the samples $Y_{k,t}$ represents the feedback obtained by the CR-equipped device after sensing the channel $k$ at time $t$.
A reward of $r(t) = 1$ indicates that no Primary User was sensed, while a reward of $r(t)=0$ indicates that the channel $k$ is busy at time $t$ and no uplink message can be sent.
%
This model was first introduced by Wassim Jouini during his PhD thesis,
in \cite{Jouini09} and later studied in both \cite{Jouini10,Jouini12}.
Proof-of-concepts using real-world radio hardware was first proposed in \cite{MoyWSR2014,RobertSDR2014}.
%
We study a similar model of using MAB for Cognitive Radio but without the OSA structre of Primary and Secondary users, \ie, without sensing information but only a collision indicator, in Chapters~\ref{chapter:4} and \ref{chapter:5}.

@@

% ----------------------------------------------------------------------------
% \section{Definition, decomposition and lower-bounds on the regret}
\section{Measuring the performance of a MAB algorithm}
% : definition, decomposition, and lower bounds
\label{sec:2:lowerUpperBoundsRegret}

@@

\subsection{Other measures of performances}
\label{sub:2:otherMeasuresPerformance}

The theoretical results obtained in this thesis are all expressed in terms of the mean regret $R_T^{\cA}$ (in Chapters~\ref{chapter:5} and \ref{chapter:6}), but we quickly mention other measures of performances used in our work.
